Hidden Talents in Context: Multiverse analysis repository

### 2022-01-18 README.Rmd
fix typos in README
CD revision 1, updaating manuscript and supplement

---
title: "Hidden Talents Multiverse Analysis"
output: github_document
---

@@

This repository contains data, code, and (some) output for a working manuscript.

@@

This directory contains the manuscript for this project. It was written in R Markdown and is 100% reproducible. The `.Rmd` fie contains the written text with all figures, tables, and in-text statistics. All outputs reported in the manuscript were staged prior to compiling into a `.pdf` document and stored in a `.Rdata` file called `staged-objects.Rdata`. The R Markdown document reads these staged files to make the overall document easier to read. The scripts that produce the staged objects are located in the `manuscript/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the manuscript.

@@

### Seconary Analyses

@@

This directory contains the supplement to the manuscript described above. The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.pdf`. The staged objects are stored in `supplement/staged-objects.Rdata`. The scripts that produce the staged objects are located in the `supplement/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the supplement.

@@

1. `1-data-prep/1-data-non-arbitrary.R`
2. `1-data-prep/2-primary-multiverse-datasets.R`
3. `1-data-prep/3-sedoncary-multiverse-datasets.R`

@@

1. `supplement/scripts/rmd-staging.R`: loads all necessary data and multiverse objects and sources the following scripts to create tables and figures for the supplement stored in `supplement/staged-objects.Rdata`:
    - `1-covariates.R`
    - `2-secondary1.R`
    - `3-secondary2.R`
    - `4-tables.R`
2. `supplement/supplement.Rmd`: loads `supplement/staged-objects.Rdata` and knits together the written supplement and all tables and figures computed by the staging script above.

>>>>

---
title: "Hidden Talents in Context: Multiverse analysis repository"
output: github_document
---

@@

This repository contains data, code, and (some) output for a manuscript entitled "Hidden talents in context: Cognitive performance with abstract versus ecological stimuli among adversity-exposed youth" submitted to and under review at *Child Development*.

@@

This directory contains the manuscript for this project. It was written in R Markdown and is 100% reproducible. The `.Rmd` fie contains the written text with all figures, tables, and in-text statistics. All outputs reported in the manuscript were staged prior to compiling into a `.docx` document and stored in a `.Rdata` file called `staged-objects.Rdata`. The R Markdown document reads these staged files to make the overall document easier to read. The scripts that produce the staged objects are located in the `manuscript/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the manuscript.

@@

### Secondary Analyses

@@

This directory contains the supplement to the manuscript described above. The supplement was produced using the same approach as the manuscript: it was written in R Markdown, is 100% reproducible, and all outputs were staged prior to compiling into a `.docx`. The staged objects are stored in `supplement/staged-objects.Rdata`. The scripts that produce the staged objects are located in the `supplement/scripts/` directory and are named to be self-explanatory. The `rmd-staging.R` script reads necessary data/objects from the `multiverse-objects/` directory and sources the other scripts to produce the objects needed for the supplement.

@@

1. `1-data-prep/1-data-non-arbitrary.R`
2. `1-data-prep/2-primary-multiverse-datasets.R`
3. `1-data-prep/3-secondary-multiverse-datasets.R`

@@

1. `supplement/scripts/rmd-staging.R`: loads all necessary data and multiverse objects and sources the following scripts to create tables and figures for the supplement stored in `supplement/staged-objects.Rdata`:
    - `1-covariates.R`
    - `2-secondary1.R`
    - `3-secondary2.R`
    - `4-tables.R`
    - `5-tables-r1.R`
2. `supplement/supplement.Rmd`: loads `supplement/staged-objects.Rdata` and knits together the written supplement and all tables and figures computed by the staging script above.
